---
title: "EuroeanOption up-and-in"
author: "Aleksandra Gawor"
date: "27 stycznia 2019"
output: html_document
---

```{r}
library("GaworAleksandra")

```

Up and in options are a type of barrier option that can only be exercised when the price of the underlying asset reaches a set barrier level. Up and in is one common type of knock in barrier option.

source: https://www.investopedia.com/terms/u/up-and-inoption.asp

```{r}
install.packages("GaworAleksandra_1.0.tar.gz",
                 type = "source",
                 repos = NULL)

```


Maximum value of my barrier is equal to 99.
When the barrier value is equal to 100 the value of an option will be equal to zero
to make the results optimal I have chosen to make the value of the barrier equal to 70

```{r}

getEuropeanPutPrice(126, 100, 95, 0.2, 0.06, 0.5, 70)
```
```{r}
McEuropean <- function (expiry) {
  return(
    getEuropeanPutPrice(126, 100, 95, 0.2, 0.06, 0.5, 70)
  )
  }

# 5. call the function
McEuropean(0.5)

# 6. arguments values of values of cunction
expiry <- seq(0.01, 1, by = 0.01)
result <- sapply(expiry, McEuropean)

# 7. same plot using ggplot2 package
library(ggplot2)
qplot(x = expiry,
      y = result,
      col = 'red',
      xlab = "time to maturity",
      ylab = "price of European put option",
      main = "price of European put option vs. time  to maturity")
```

